Trump vs. Harris: A 2024 US Presidential Elections Modelling Forecast

### 2024-11-04 paper/paper.qmd
Updated paper to include copy of survey

```{r}
#| label: fig-candidatepercentage
#| fig-cap: violin plot displaying the percentage of support Harris and Trump receive compared to all candidates
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-pollrecency
#| fig-cap: The distribution of how recent a poll was conducted
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-corrmatrix
#| fig-cap: correlation between PollScore, the sample size of the poll, and the percentage of support for a candidate
#| echo: false
#| eval: true
#| warning: false
#| message: false
numerical_data <- cleaned_data %>%
  select(PollScore, SampleSize, PollRecency, NumericGrade)

@@

```{r}
#| label: tbl-sum
#| tbl-cap: summary statistics for the cleaned data
#| echo: false
#| eval: true
#| warning: false
#| message: false
cleaned_data <- read_parquet(here::here("data/analysis_data/president_polls_cleaned.parquet"))

@@

@@

>>>>

```{r}
#| label: fig-candidatepercentage
#| fig-cap: Violin plot displaying the percentage of support Harris and Trump receive compared to all candidates
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-pollrecency
#| fig-cap: The distribution of how recently a poll was conducted
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-corrmatrix
#| fig-cap: The correlation between the numerical predictor variables and the percentage of support for a candidate
#| echo: false
#| eval: true
#| warning: false
#| message: false
numerical_data <- cleaned_data %>%
  select(PollScore, SampleSize, PollRecency, NumericGrade)

@@

```{r}
#| label: tbl-sum
#| tbl-cap: Summary statistics for the cleaned poll data
#| echo: false
#| eval: true
#| warning: false
#| message: false
cleaned_data <- read_parquet(here::here("data/analysis_data/president_polls_cleaned.parquet"))

@@

## Idealized Survey

@@

**2024 US Presidential Election Forecast Survey**

**Conducted by:** Sophia Brothers, Deyi Kong, and Rayan Awad Alim\
**Contact:** sophia.brothers\@mail.utoronto.ca

Welcome, and thank you for taking part in the **2024 US Presidential Election Forecast Survey**. Your participation will help us gain insights into voter preferences, influential issues, and factors shaping the election across all 50 states and Washington D.C.

As a thank you for your time, all survey respondents will be automatically entered into a sweepstakes, with a **chance to win \$500**. One winner will be selected from each state and Washington D.C.

**Your responses will remain strictly confidential** and anonymous, and any data collected will be securely stored and used solely for academic and analytical purposes. No identifying information will be connected to your survey responses.

------------------------------------------------------------------------

**Section 1: Demographics**

**State of Residence**\
- \[List of all 50 states and Washington D.C.\]

**Zip Code**

**Age**\
1. 18-24\
2. 25-34\
3. 35-44\
4. 45-54\
5. 55-64\
6. 65+

**Gender**\
1. Male\
2. Female\
3. Non-binary/Other\
4. Prefer not to say

**Race/Ethnicity**\
- White\
- Black or African American\
- Hispanic or Latino\
- Asian\
- Native American or Alaska Native\
- Native Hawaiian or Pacific Islander\
- Other\
- Prefer not to say

**Income Level**\
- Less than \$25,000\
- \$25,000 - \$49,999\
- \$50,000 - \$74,999\
- \$75,000 - \$99,999\
- \$100,000 - \$149,999\
- \$150,000 or more

**Highest Level of Education**\
- Less than high school\
- High school diploma or equivalent\
- Some college, no degree\
- Associate degree\
- Bachelor’s degree\
- Graduate or professional degree

**Party Affiliation**\
- Republican\
- Democrat\
- Independent\
- Other

------------------------------------------------------------------------

**Section 2: Voter Registration**

**Are you registered to vote in the upcoming election?**\
- Yes\
- No

**How likely are you to vote in the upcoming election?**\
1 (Very Unlikely) to 5 (Very Likely)

------------------------------------------------------------------------

**Section 3: Voting Intent**

**If the election were held today, who would you vote for?**\
- Kamala Harris\
- Donald Trump\
- Other

**How certain are you of your choice?**\
1 (Not Certain at All) to 5 (Very Certain)

**How likely are you to vote on election day?**\
1 (Not Likely) to 5 (Very Likely)

------------------------------------------------------------------------

**Section 4: Key Issues**

**Rank the most important issues influencing your vote:**\
- Economy\
- Healthcare\
- Immigration\
- Climate Change\
- National Security\
- Social Issues (e.g., LGBTQ+ rights, abortion)\
- Education\
- Taxes\
- Gun Control\
- Foreign Policy\
- Public Safety\
- Infrastructure

------------------------------------------------------------------------

**Section 5: Candidate Perception**

**Rate the following candidates on Trustworthiness:**\
- Kamala Harris: Very low, Low, Neutral, High, Very high\
- Donald Trump: Very low, Low, Neutral, High, Very high

**Rate the following candidates on Competence:**\
- Kamala Harris: Very low, Low, Neutral, High, Very high\
- Donald Trump: Very low, Low, Neutral, High, Very high

**Rate the following candidates on Leadership:**\
- Kamala Harris: Very low, Low, Neutral, High, Very high\
- Donald Trump: Very low, Low, Neutral, High, Very high

------------------------------------------------------------------------

**Section 6: Prior Voting History**

**Did you vote in the last presidential election?**\
- Yes\
- No

**If yes, who did you vote for?**\
- Joe Biden\
- Donald Trump\
- Other

------------------------------------------------------------------------

Thank you for your time and participation! Your responses will help us understand the key issues shaping the upcoming election. As a reminder, all participants are automatically entered into a sweepstakes for a chance to win \$500, with one winner selected from each state and Washington D.C.
